---
title: "A Reproduction of 'Newspapers in Times of Low Advertising Revenues'"
author: "Jin Long Cao"
date: "12/11/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(haven)
```

```{r data, echo=FALSE}
a <- read_dta("116438-V1/Angelucci_Cage_AEJMicro_dataset.dta")
b <- read_dta("116438-V1/Angelucci_Cage_AEJMicro_Descriptive_evidence_advertisement.dta")
c <- read_dta("116438-V1/Angelucci_Cage_AEJMicro_Descriptive_evidence_advertising_industry.dta")
d <- read_dta("116438-V1/Angelucci_Cage_AEJMicro_Descriptive_evidence_television_quality.dta")
e <- read_dta("116438-V1/Angelucci_Cage_AEJMicro_Descriptive_evidence_US.dta")
```

## Keywords

## Abstract

## Introduction
In this paper we attempt to reproduce 'Newspapers in Times of Low Advertising Revenues' by Charles Angelucci and Julia Cage. We find…


## Data

## Model

## Discussion

# Limitation and Weaknesses

# Future Work

## Appendix
The code, scripts, and RMarkdown file in this report’s analysis can also be found at the following link:
https://github.com/JinLong-Cao/A-Reproduction-of-Newspapers-in-Times-of-Low-Advertising-Revenues-

## Reference

- Angelucci, Charles, and Cagé, Julia. Replication data for: Newspapers in Times of Low Advertising Revenues. Nashville, TN: American Economic Association [publisher], 2019. Ann Arbor, MI: Inter-university Consortium for Political and Social Research [distributor], 2019-12-07. https://doi.org/10.3886/E116438V1


